Gut microbes and their genes are associated with cognition and neuroanatomy in children

### 2023-03-01 manuscript/main.tex
fix up tables 3-5

@@

>>>>

\begin{table}
    \begin{tabular}{|r|r|r|r|r|}
      \hline\hline
      \textbf{Subject Ages (months)} & \textbf{Microbial feature} & \textbf{Demo.} & \textbf{Test set correlation (± C.I.)} & \textbf{Test set RMSE (± C.I.)} \\\hline
      \multirow{5}{*}{0 to 6} & - & + & 13.01 ± 0.05 & -0.14 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{taxa} & - & 12.66 ± 0.05 & -0.1 ± 0.01 \\ \cline{3-5}
            &       & + & 12.7 ± 0.05 & -0.12 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 12.56 ± 0.05 & -0.01 ± 0.01 \\ \cline{3-5}
            &       & + & 12.56 ± 0.05 & -0.02 ± 0.01 \\ \cline{1-5}
      \multirow{5}{*}{18 to 120} & - & + & 16.27 ± 0.04 & 0.506 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{taxa} & - & 17.66 ± 0.04 & 0.363 ± 0.003 \\ \cline{3-5}
            &       & + & 17.29 ± 0.04 & 0.429 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 18.01 ± 0.04 & 0.303 ± 0.003 \\ \cline{3-5}
            &       & + & 17.86 ± 0.04 & 0.333 ± 0.004 \\\hline\hline
    \end{tabular}
\end{table}

@@

\begin{table}
    \begin{tabular}{rrrr}
      \hline\hline
      \textbf{Input set} & \textbf{Age bracket} & \textbf{Microbiome encoding type} & \textbf{Demographics Provided? (sex, education)} \\\hline
      1 & \multirow{5}{*}{0 to 6 months} & Not provided & yes \\
      2 &  & \multirow{2}{*}{Taxonomic profile} & no \\
      3 &  &  & yes \\
      4 &  & \multirow{2}{*}{Functional Profile (ECs)} & no \\
      5 &  &  & yes \\
      6 & \multirow{5}{*}{18 to 120 months} & Not provided & yes \\
      7 &  & \multirow{2}{*}{Taxonomic profile} & no \\
      8 &  &  & yes \\
      9 &  & \multirow{2}{*}{Functional Profile (ECs)} & no \\
      10 &  &  & yes \\\hline\hline
    \end{tabular}
\end{table}
